---
title: "World Happiness Report 2019"
author: "Chun-Li Hou"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Content

- [Introduction](#1)
    - [Background](#1.1)
    - [Mission](#1.2)
- [Preparation](#2)
    - [Environment](#2.1)
    - [Dataset](#2.2)
- [Visualization](#3)
    - [Correlation plot](#3.1)
    - [Comparing different continents regarding their happiness variables](#3.2)
    - [Correlation plot for each continent](#3.3)
    - [Happiness score comparison on different continents](#3.4)
    - [Scatter plot with regression line](#3.5)
    - [Scatter plot colored by Continents](#3.6)
    - [3D Plot](#3.7)
- [Prediction](#4)
    - [Partition](#4.1)
    - [Machine learning algorithms](#4.2)
        - [Multiple Linear Regression](#4.2.1)
        - [Support Vector Regression](#4.2.2)
        - [Decision Tree](#4.2.3)
        - [Random Forest](#4.2.4)
        - [Neural Net](#4.2.5)
    - [Evaluation](#4.3)
- [Conclusion](#5)
- [Reference](#6)

## Introduction <a name = "1"></a>

### Background <a name = "1.1"></a>

The dataset is happiness 2019 dataset. It comes from Kaggle's dataset. This dataset gives the happiness rank and happiness score of 156 countries around the world based on seven factors, including family, life expectancy, economy, generosity, trust in government, freedom, and dystopia residual. Sum of the value of these seven factors gives us the happiness score. So, it is evident that the higher value of each of these seven factors means the level of happiness is higher.

### Mission <a name = "1.2"></a>

The purpose of choosing the work is to find out which factors are more important to live a happier life. As a result, people and countries can focus on the more significant factors to achieve a higher happiness level. We also implement several machine learning algorithms to predict the happiness score and compare the result to discover which algorithm works better for this specific dataset.

## Preparation <a name = "2"></a>

### Environment <a name = "2.1"></a>

```{r, message = FALSE}
# setting gotop
gotop::use_gotop()

# loading packages
if(!require("pacman")) install.packages("pacman")
pacman::p_load(plyr, dplyr, tidyverse, lubridate, caTools, ggplot2, ggthemes, reshape2, data.table, tidyr,
               corrgram, corrplot, formattable, cowplot, ggpubr, plot3D, RColorBrewer, rgl, car, plotly, 
               caTools, forecast, e1071, rpart, rpart.plot, rattle, randomForest, neuralnet)
```

### Dataset <a name = "2.2"></a>

```{r}
# importing dataset
df.0 = read.csv("2019.csv")
df.1 = df.0[, c(2, 1, 3, 4, 5, 6, 7, 8, 9)]

# renaming columns
colnames(df.1) = c("Country",
                   "Happiness.Rank",
                   "Happiness.Score",
                   "Economy",
                   "Family",
                   "Life.Expectancy",
                   "Freedom",
                   "Generosity",
                   "Trust")

# creating a new column for continents
df.1$Continent = NA

# Asia
df.1$Continent[which(df.1$Country %in% c("Israel", "United Arab Emirates", "Singapore", "Thailand",
                                         "Taiwan", "Qatar", "Saudi Arabia", "Kuwait", "Bahrain", 
                                         "Malaysia", "Uzbekistan", "Japan", "South Korea", "Turkmenistan",
                                         "Kazakhstan", "Turkey", "Hong Kong", "Philippines", "Jordan",
                                         "China", "Pakistan", "Indonesia", "Azerbaijan", "Lebanon",
                                         "Vietnam", "Tajikistan", "Bhutan", "Kyrgyzstan", "Nepal", 
                                         "Mongolia", "Palestinian Territories", "Iran", "Bangladesh",
                                         "Myanmar", "Iraq", "Sri Lanka", "Armenia", "India", "Georgia",
                                         "Cambodia", "Afghanistan", "Yemen", "Syria", "Laos", 
                                         "Northern Cyprus"))] = "Asia"
# Europe
df.1$Continent[which(df.1$Country %in% c("Norway", "Denmark", "Iceland", "Switzerland", "Finland",
                                         "Netherlands", "Sweden", "Austria", "Ireland", "Germany",
                                         "Belgium", "Luxembourg", "United Kingdom", "Czech Republic",
                                         "Malta", "France", "Spain", "Slovakia", "Poland", "Italy",
                                         "Russia", "Lithuania", "Latvia", "Moldova", "Romania",
                                         "Slovenia", "North Cyprus", "Cyprus", "Estonia", "Belarus",
                                         "Serbia", "Hungary", "Croatia", "Kosovo", "Montenegro",
                                         "Greece", "Portugal", "Bosnia and Herzegovina", "Macedonia",
                                         "Bulgaria", "Albania", "Ukraine", "North Macedonia"))] = "Europe"
# North America
df.1$Continent[which(df.1$Country %in% c("Canada", "Costa Rica", "United States", "Mexico", "Panama", 
                                         "El Salvador", "Belize", "Guatemala", "Jamaica", "Nicaragua",
                                         "Dominican Republic", "Honduras", "Haiti"))] = "North America"
# South America
df.1$Continent[which(df.1$Country %in% c("Chile", "Brazil", "Argentina", "Uruguay", "Colombia", "Ecuador",
                                         "Bolivia", "Peru", "Paraguay", "Venezuela", 
                                         "Trinidad & Tobago"))] = "South America"
# Australia
df.1$Continent[which(df.1$Country %in% c("New Zealand", "Australia"))] = "Australia"

# Africa
df.1$Continent[which(is.na(df.1$Continent))] = "Africa"

# reordering columns
df.2 = df.1[, c(1, 10, 2, 3, 4, 5, 6, 7, 8, 9)]

# encoding factor columns
df.2$Country = as.factor(df.2$Country)
df.2$Continent = as.factor(df.2$Continent)

# attaching dataset
attach(df.2)
glimpse(df.2)
```

1. Country: Name of countries
2. Happiness.Rank: Rank of the country based on the Happiness Score
3. Happiness.Score: Happiness measurement on a scale of 0 to 10
4. Economy: GDP per captia is a measure of the total output of a country that takes the gross domestic product (GDP) and divides it by the number of people in that country
5. Family: Importance of having a family
6. Life.Expectancy: Importance of health and amount of time prople expect to live
7. Freedom: Importance of freedom in each country
8. Generosity: The quality of being kind and generous
9. Trust: Perception of corruption in a government

## Visualization <a name = "3"></a>

### Correlation plot <a name = "3.1"></a>

```{r}
# finding the correlation between numerical columns
num.cols = sapply(df.2, is.numeric)
cor.data = cor(df.2[, num.cols])
col = colorRampPalette(c("#BB4444", "#EE9988", "#FFFFFF", "#77AADD", "#4477AA"))
corrplot(cor.data, method = "color", col = col(200), 
         type = "lower", addCoef.col = "black", tl.col = "black", tl.cex = 0.7)
```

```{r}
# removing happiness.rank
cor.data = cor(df.2[, c(4:10)])
corrplot(cor.data, method = "color", col = col(200), 
         type = "lower", addCoef.col = "black", tl.col = "black", tl.cex = 0.7)
```

According to the above correlation plot, Economy, Family, and Life.Expectancy play the most significant role in contributing to happiness. Trust and Generosity have the lowest impact on the happiness score.

### Comparing different continents regarding their happiness variables <a name = "3.2"></a>

```{r, message = FALSE, warning = FALSE}
# aggregating by continent
df.2.continent = df.2 %>% select(-3) %>% group_by(Continent) %>% 
    summarise_at(vars(-Country), funs(mean(., na.rm = T)))

# melting
df.2.melt = melt(df.2.continent)

# faceting
ggplot(df.2.melt, aes(y = value, x = Continent, color = Continent, fill = Continent)) +
    geom_bar(stat = "identity") +
    facet_wrap(~variable) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3)) +
    labs(title = "Average value of happiness variables for different continents", y = "Average value")
```

We can see that Australia has approximately the highest average in all fields. After Australia, Europe, North America, and South America are roughly the same as the second. Finally, Asia and Africa have the lowest scores in all fields.

### Correlation plot for each continent <a name = "3.3"></a>

```{r}
par(mfrow = c(2, 3))
cor.data = cor(df.2[df.2$Continent == "Africa", c(4:10)])
corrplot(cor.data, method = "color", col = brewer.pal(n = 7, name = "RdBu"), addgrid.col = "black",
         type = "lower", tl.col = "black", tl.cex = 0.7)
cor.data = cor(df.2[df.2$Continent == "Asia", c(4:10)])
corrplot(cor.data, method = "color", col = brewer.pal(n = 7, name = "RdBu"), addgrid.col = "black",
         type = "lower", tl.col = "black", tl.cex = 0.7)
cor.data = cor(df.2[df.2$Continent == "Australia", c(4:10)])
corrplot(cor.data, method = "color", col = brewer.pal(n = 7, name = "RdBu"), addgrid.col = "black",
         type = "lower", tl.col = "black", tl.cex = 0.7)
cor.data = cor(df.2[df.2$Continent == "Europe", c(4:10)])
corrplot(cor.data, method = "color", col = brewer.pal(n = 7, name = "RdBu"), addgrid.col = "black",
         type = "lower", tl.col = "black", tl.cex = 0.7)
cor.data = cor(df.2[df.2$Continent == "North America", c(4:10)])
corrplot(cor.data, method = "color", col = brewer.pal(n = 7, name = "RdBu"), addgrid.col = "black",
         type = "lower", tl.col = "black", tl.cex = 0.7)
cor.data = cor(df.2[df.2$Continent == "South America", c(4:10)])
corrplot(cor.data, method = "color", col = brewer.pal(n = 7, name = "RdBu"), addgrid.col = "black",
         type = "lower", tl.col = "black", tl.cex = 0.7)
```

- Correlation between "Happiness Score" and other variables in Africa:
1. Positive contribution: Economy = Family > Life.Expectancy = Freedom
2. Negative contribution: Generosity = Trust

- Correlation between "Happiness Score" and other variables in Aisa:
1. Positive contribution: Economy > Family = Life.Expectancy = Freedom > Trust
2. No contribution: **Generosity**

- Correlation between "Happiness Score" and other variables in Australia:  
1. No meaning due to only 2 countries in the group

- Correlation between "Happiness Score" and other variables in Europe:
1. Positive contribution: Economy = Freedom = Trust > Family = Life.Expectancy = **Generosity**

- Correlation between "Happiness Score" and other variables in North America:
1. Positive contribution: Economy = Family = Life.Expectancy = Freedom > Trust
2. Negative contribution: **Generosity**

- Correlation between "Happiness Score" and other variables in South America:
1. Positive contribution: Economy = Generosity = Freedom > Trust = Life.Expectancy
2. No contribution: **Family**

### Happiness score comparison on different continents <a name = "3.4"></a>

```{r}
# plot
ggplot(df.2, aes(x = Continent, y = Happiness.Score)) +
    geom_violin(aes(fill = Continent), alpha = 0.7) +
    geom_jitter(alpha = 0.5, size = 0.7, width = 0.05) +
    theme_bw() +
    labs(title = "Value of happiness variables in different continents", y = "Value", x = NULL) +
    theme(plot.title = element_text(face = "bold", size = (15)),
          axis.title = element_text(size = (10)))
```

```{r, message = FALSE, warning = FALSE, fig.width = 8, fig.height = 2}
# table
stable = desc_statby(df.2, measure.var = "Happiness.Score", grps = "Continent")
stable %>% mutate(across(is.numeric, ~ round(., 2))) %>% ggtexttable(rows = NULL, theme = ttheme("classic"))
# length: the number of elements in each group
# min: minimum
# max: maximum
# median: median
# mean: mean
# iqr: interquartile range
# mad: median absolute deviation (see ?MAD)
# sd: standard deviation of the mean
# se: standard error of the mean
# ci: confidence interval of the mean
# range: the range = max - min
# cv: coefficient of variation, sd/mean
# var: variance, sd^2
```

As for the median of "Happiness Score":

1. Australia
2. North America
3. Europe
4. South America
5. Asia
6. Africa

### Scatter plot with regression line <a name = "3.5"></a>

```{r, message = FALSE, warning = FALSE}
# happiness score vs life expectancy 
ggplot(df.2, aes(x = Life.Expectancy, y = Happiness.Score)) +
    geom_point(aes(color = Continent), size = 2, alpha = 0.8) +
    geom_smooth(aes(color = Continent, fill = Continent), method = "lm", fullrange = T) +
    facet_wrap(~Continent) +
    theme_bw() +
    labs(title = "Scatter plot with regression line")
```

```{r, message = FALSE, warning = FALSE}
# happiness score vs economy 
ggplot(df.2, aes(x = Economy, y = Happiness.Score)) +
    geom_point(aes(color = Continent), size = 2, alpha = 0.8) +
    geom_smooth(aes(color = Continent, fill = Continent), method = "lm", fullrange = T) +
    facet_wrap(~Continent) +
    theme_bw() +
    labs(title = "Scatter plot with regression line")
```

```{r, message = FALSE, warning = FALSE}
# happiness score vs family 
ggplot(df.2, aes(x = Family, y = Happiness.Score)) +
    geom_point(aes(color = Continent), size = 2, alpha = 0.8) +
    geom_smooth(aes(color = Continent, fill = Continent), method = "lm", fullrange = T) +
    facet_wrap(~Continent) +
    theme_bw() +
    labs(title = "Scatter plot with regression line")
```

```{r, message = FALSE, warning = FALSE}
# happiness score vs freedom 
ggplot(df.2, aes(x = Freedom, y = Happiness.Score)) +
    geom_point(aes(color = Continent), size = 2, alpha = 0.8) +
    geom_smooth(aes(color = Continent, fill = Continent), method = "lm", fullrange = T) +
    facet_wrap(~Continent) +
    theme_bw() +
    labs(title = "Scatter plot with regression line")
```

```{r, message = FALSE, warning = FALSE}
# happiness score vs generosity 
ggplot(df.2, aes(x = Generosity, y = Happiness.Score)) +
    geom_point(aes(color = Continent), size = 2, alpha = 0.8) +
    geom_smooth(aes(color = Continent, fill = Continent), method = "lm", fullrange = T) +
    facet_wrap(~Continent) +
    theme_bw() +
    labs(title = "Scatter plot with regression line")
```

```{r, message = FALSE, warning = FALSE}
# happiness score vs trust 
ggplot(df.2, aes(x = Trust, y = Happiness.Score)) +
    geom_point(aes(color = Continent), size = 2, alpha = 0.8) +
    geom_smooth(aes(color = Continent, fill = Continent), method = "lm", fullrange = T) +
    facet_wrap(~Continent) +
    theme_bw() +
    labs(title = "Scatter plot with regression line")
```

Correlaton with "Happiness Score":

- Life.Expectancy: North America (Most positive correlation)
- Economy: Europe (Most positive correlation)
- Family: South America (Only one no correlation)
- Freedom: North America (Most positive correlation)
- Generosity: North America (Most negative correlation)
- Trust: Africa (Most negative correlation)

### Scatter plot colored by Continents <a name = "3.6"></a>

```{r, fig.width = 15, fig.height = 10}
# Life.Expectancy
sp = ggscatter(df.2, x = "Life.Expectancy", y = "Happiness.Score",
               color = "Continent", palette = "jco",
               size = 2, alpha = 0.6)
xbp = ggboxplot(df.2$Life.Expectancy, width = 0.3, fill = "lightgray") +
    rotate() +
    theme_transparent()
ybp = ggboxplot(df.2$Happiness.Score, width = 0.3, fill = "lightgray") +
    theme_transparent()
xbp_grob = ggplotGrob(xbp)
ybp_grob = ggplotGrob(ybp)
xmin = min(df.2$Life.Expectancy); xmax = max(df.2$Life.Expectancy)
ymin = min(df.2$Happiness.Score); ymax = max(df.2$Happiness.Score)
yoffset = (1/15)*ymax; xoffset = (1/15)*xmax
p.1 = sp + annotation_custom(grob = xbp_grob, xmin = xmin, xmax = xmax, 
                             ymin = ymin-yoffset, ymax = ymin+yoffset) +
    annotation_custom(grob = ybp_grob,
                      xmin = xmin-xoffset, xmax = xmin+xoffset, 
                      ymin = ymin, ymax = ymax)

# Economy
sp = ggscatter(df.2, x = "Economy", y = "Happiness.Score",
               color = "Continent", palette = "jco",
               size = 2, alpha = 0.6)
xbp = ggboxplot(df.2$Economy, width = 0.3, fill = "lightgray") +
    rotate() +
    theme_transparent()
ybp = ggboxplot(df.2$Happiness.Score, width = 0.3, fill = "lightgray") +
    theme_transparent()
xbp_grob = ggplotGrob(xbp)
ybp_grob = ggplotGrob(ybp)
xmin = min(df.2$Economy); xmax = max(df.2$Economy)
ymin = min(df.2$Happiness.Score); ymax = max(df.2$Happiness.Score)
yoffset = (1/15)*ymax; xoffset = (1/15)*xmax
p.2 = sp + annotation_custom(grob = xbp_grob, xmin = xmin, xmax = xmax, 
                             ymin = ymin-yoffset, ymax = ymin+yoffset) +
    annotation_custom(grob = ybp_grob,
                      xmin = xmin-xoffset, xmax = xmin+xoffset, 
                      ymin = ymin, ymax = ymax)

# Family
sp = ggscatter(df.2, x = "Family", y = "Happiness.Score",
               color = "Continent", palette = "jco",
               size = 2, alpha = 0.6)
xbp = ggboxplot(df.2$Family, width = 0.3, fill = "lightgray") +
    rotate() +
    theme_transparent()
ybp = ggboxplot(df.2$Happiness.Score, width = 0.3, fill = "lightgray") +
    theme_transparent()
xbp_grob = ggplotGrob(xbp)
ybp_grob = ggplotGrob(ybp)
xmin = min(df.2$Family); xmax = max(df.2$Family)
ymin = min(df.2$Happiness.Score); ymax = max(df.2$Happiness.Score)
yoffset = (1/15)*ymax; xoffset = (1/15)*xmax
p.3 = sp + annotation_custom(grob = xbp_grob, xmin = xmin, xmax = xmax, 
                             ymin = ymin-yoffset, ymax = ymin+yoffset) +
    annotation_custom(grob = ybp_grob,
                      xmin = xmin-xoffset, xmax = xmin+xoffset, 
                      ymin = ymin, ymax = ymax)

# Freedom
sp = ggscatter(df.2, x = "Freedom", y = "Happiness.Score",
               color = "Continent", palette = "jco",
               size = 2, alpha = 0.6)
xbp = ggboxplot(df.2$Freedom, width = 0.3, fill = "lightgray") +
    rotate() +
    theme_transparent()
ybp = ggboxplot(df.2$Happiness.Score, width = 0.3, fill = "lightgray") +
    theme_transparent()
xbp_grob = ggplotGrob(xbp)
ybp_grob = ggplotGrob(ybp)
xmin = min(df.2$Freedom); xmax = max(df.2$Freedom)
ymin = min(df.2$Happiness.Score); ymax = max(df.2$Happiness.Score)
yoffset = (1/15)*ymax; xoffset = (1/15)*xmax
p.4 = sp + annotation_custom(grob = xbp_grob, xmin = xmin, xmax = xmax, 
                             ymin = ymin-yoffset, ymax = ymin+yoffset) +
    annotation_custom(grob = ybp_grob,
                      xmin = xmin-xoffset, xmax = xmin+xoffset, 
                      ymin = ymin, ymax = ymax)

# Generosity
sp = ggscatter(df.2, x = "Generosity", y = "Happiness.Score",
               color = "Continent", palette = "jco",
               size = 2, alpha = 0.6)
xbp = ggboxplot(df.2$Generosity, width = 0.3, fill = "lightgray") +
    rotate() +
    theme_transparent()
ybp = ggboxplot(df.2$Happiness.Score, width = 0.3, fill = "lightgray") +
    theme_transparent()
xbp_grob = ggplotGrob(xbp)
ybp_grob = ggplotGrob(ybp)
xmin = min(df.2$Generosity); xmax = max(df.2$Generosity)
ymin = min(df.2$Happiness.Score); ymax = max(df.2$Happiness.Score)
yoffset = (1/15)*ymax; xoffset = (1/15)*xmax
p.5 = sp + annotation_custom(grob = xbp_grob, xmin = xmin, xmax = xmax, 
                             ymin = ymin-yoffset, ymax = ymin+yoffset) +
    annotation_custom(grob = ybp_grob,
                      xmin = xmin-xoffset, xmax = xmin+xoffset, 
                      ymin = ymin, ymax = ymax)

# Trust
sp = ggscatter(df.2, x = "Trust", y = "Happiness.Score",
               color = "Continent", palette = "jco",
               size = 2, alpha = 0.6)
xbp = ggboxplot(df.2$Trust, width = 0.3, fill = "lightgray") +
    rotate() +
    theme_transparent()
ybp = ggboxplot(df.2$Happiness.Score, width = 0.3, fill = "lightgray") +
    theme_transparent()
xbp_grob = ggplotGrob(xbp)
ybp_grob = ggplotGrob(ybp)
xmin = min(df.2$Trust); xmax = max(df.2$Trust)
ymin = min(df.2$Happiness.Score); ymax = max(df.2$Happiness.Score)
yoffset = (1/15)*ymax; xoffset = (1/15)*xmax
p.6 = sp + annotation_custom(grob = xbp_grob, xmin = xmin, xmax = xmax, 
                             ymin = ymin-yoffset, ymax = ymin+yoffset) +
    annotation_custom(grob = ybp_grob,
                      xmin = xmin-xoffset, xmax = xmin+xoffset, 
                      ymin = ymin, ymax = ymax)

ggarrange(p.1, p.2, p.3, p.4, p.5, p.6, nrow = 2, ncol = 3)
```

We can know in a picture that "Happiness Score" has postive correlation with Life.Expectancy, Economy, Family, and Freedom, but has no correlation with Generosity and Trust.

### 3D Plot <a name = "3.7"></a>

```{r, fig.width = 6, fig.height = 6}
# 3D plot
scatter3D(x = df.2$Life.Expectancy, y = df.2$Economy, z = df.2$Happiness.Score, 
          colvar = as.integer(df.2$Continent), col = brewer.pal(n = 6, name = "Spectral"),
          bty = "b2", phi = 0, pch = 20, type = "h", cex = 1, ticktype = "simple",
          colkey = list(at = c(1.40, 2.25, 3.1, 3.9, 4.75, 5.60), labels = levels(df.2$Continent),
                        width = 0.5, side = 1, cex.axis = 0.6),
          main = "Happiness data", xlab = "Life.Expectancy", ylab ="Economy", zlab = "Happiness.Score")
# text3D(x = df.2$Life.Expectancy, y = df.2$Economy, z = df.2$Happiness.Score,
#        labels = df.2$Country, add = T, colkey = F, cex = 0.6, alpha = 0.5)
```

```{r, fig.width = 6, fig.height = 6}
# 3D plot with projection
scatter3D_fancy = function(x, y, z, ..., group)
{
    panelfirst = function(pmat) {
        XY = trans3D(x, y, z = rep(min(z), length(z)), pmat = pmat)
        scatter2D(XY$x, XY$y, colvar = group, pch = ".", col = brewer.pal(n = 6, name = "Spectral"),
                  cex = 2, add = T, colkey = F)
        XY = trans3D(x = rep(min(x), length(x)), y, z, pmat = pmat)
        scatter2D(XY$x, XY$y, colvar = group, pch = ".", col = brewer.pal(n = 6, name = "Spectral"),
                  cex = 2, add = T, colkey = F)
    }
    scatter3D(x, y, z, ..., colvar = group, col = brewer.pal(n = 6, name = "Spectral"),
              panel.first = panelfirst,
              colkey = list(at = c(1.40, 2.25, 3.1, 3.9, 4.75, 5.60), labels = levels(df.2$Continent),
                            width = 0.5, side = 1, cex.axis = 0.6)) 
}
scatter3D_fancy(x = df.2$Life.Expectancy, y = df.2$Economy, z = df.2$Happiness.Score, 
                group = as.integer(df.2$Continent), pch = 16, theta = 15, d = 2,
                main = "Happiness data", xlab = "Life.Expectancy", ylab ="Economy", zlab = "Happiness.Score")
```

```{r, fig.width = 8, fig.height = 8}
# interactive 3D plot with plane
scatter3d(x = df.2$Economy, y = df.2$Happiness.Score, z = df.2$Family,
          groups = df.2$Continent, axis.scales = F, grid = F,
          xlab = "Economy", ylab ="Happiness.Score", zlab = "Family")
rglwidget()
```

According to the multiple linear regression result, we can know the most significant estimates are Family and Economy. As considering a set of Family and Economy variables, we can have each continent with its Happiness.Score in a plane. We can tell Australia is the happiest and Asia the unhappiest based on only considering its social support and country economy.

```{r, fig.width = 8, fig.height = 8}
# interactive 3D plot with plane
scatter3d(x = df.2$Generosity, y = df.2$Happiness.Score, z = df.2$Trust,
          groups = df.2$Continent, axis.scales = F, grid = F,
          xlab = "Generosity", ylab ="Happiness.Score", zlab = "Trust")
rglwidget()
```

According to the multiple linear regression result, we can know Generosity and Trust are not significant. We can tell this finding also by the slope of the plane. Also, we can know Africa is the unhappiest in terms of considering its government corruption and public generosity.

```{r, fig.width = 8, fig.height = 8}
# interactive 3D plot with point
plot_ly(x = df.2$Life.Expectancy, y = df.2$Economy, z = df.2$Happiness.Score,
        type = "scatter3d", color = df.2$Continent, mode = "markers") %>%
    add_trace(text = df.2$Country, hoverinfo = "text", showlegend = F) %>% 
    layout(title = "Happiness data", 
           scene = list(xaxis = list(title = "LE"), 
                        yaxis = list(title = "EC"), 
                        zaxis = list(title = "HS"),
                        annotations = list(list(x = df.2$Life.Expectancy[which(df.2$Country == "Taiwan")], 
                                                y = df.2$Economy[which(df.2$Country == "Taiwan")], 
                                                z = df.2$Happiness.Score[which(df.2$Country == "Taiwan")], 
                                                text = "Taiwan", arrowhead = 1, 
                                                xanchor = "left", yanchor = "bottom", opacity = 0.7))))
```

## Prediction <a name = "4"></a>

### Partition <a name = "4.1"></a>

```{r}
set.seed(123)
dataset = df.2[, 4:10]
split = sample.split(dataset$Happiness.Score, SplitRatio = 0.8)
train.set = subset(dataset, split == T)
test.set = subset(dataset, split == F)
```

### Machine learning algorithms <a name = "4.2"></a>

#### Multiple Linear Regression <a name = "4.2.1"></a>

```{r}
reg.mlr = lm(formula = Happiness.Score ~ .,
             data = train.set)
summary(reg.mlr)
```

The summary shows that Economy, Family, Life.Expectancy, and Freedom have a significant impact. The adjusted R squared is 0.7611. The 76% of the dependent variable (Happiness.Score) can be explained by the model’s inputs (the independent variables).

```{r}
pred.mlr = predict(reg.mlr, newdata = test.set)
pred.actual.mlr = as.data.frame(cbind(Prediction = pred.mlr, Actual = test.set$Happiness.Score))
error = accuracy(pred.mlr, test.set$Happiness.Score)
rmse.mlr = format(round(error[2], 4), nsmall = 4) %>% as.numeric()
gg.mlr = ggplot(pred.actual.mlr, aes(x = Actual, y = Prediction)) +
    geom_point() + theme_bw() + geom_abline() +
    labs(title = "Multiple Linear Regression", subtitle = paste0("RMSE: ", rmse.mlr),
         x = "Actual happiness score", y = "Predicted happiness score") +
    theme(plot.title = element_text(face = "bold", size = (15)),
          plot.subtitle = element_text(size = (10)),
          axis.title = element_text(size = (10)))
gg.mlr
```

#### Support Vector Regression <a name = "4.2.2"></a>

```{r}
reg.svr = svm(formula = Happiness.Score ~ .,
              data = train.set,
              type = "eps-regression",
              kernel = "radial")
```

```{r}
pred.svr = predict(reg.svr, newdata = test.set)
pred.actual.svr = as.data.frame(cbind(Prediction = pred.svr, Actual = test.set$Happiness.Score))
error = accuracy(pred.svr, test.set$Happiness.Score)
rmse.svr = format(round(error[2], 4), nsmall = 4) %>% as.numeric()
gg.svr = ggplot(pred.actual.svr, aes(x = Actual, y = Prediction)) +
    geom_point() + theme_bw() + geom_abline() +
    labs(title = "Support Vector Regression", subtitle = paste0("RMSE: ", rmse.svr),
         x = "Actual happiness score", y = "Predicted happiness score") +
    theme(plot.title = element_text(face = "bold", size = (15)),
          plot.subtitle = element_text(size = (10)),
          axis.title = element_text(size = (10)))
gg.svr
```

#### Decision Tree <a name = "4.2.3"></a>

```{r}
reg.dt = rpart(formula = Happiness.Score ~ .,
               data = train.set,
               control = rpart.control(minisplit = 10))
```

```{r, fig.width = 12, fig.height = 4}
# generating rule table for all countries in the world 156
reg.dt.all = rpart(formula = Happiness.Score ~ ., data = dataset, control = rpart.control(minisplit = 10))
rpart.rules(reg.dt.all, cover = T, roundint = F) %>% ggtexttable(rows = NULL, theme = ttheme("classic"))
```

As taking an example, the Happiness.Score is 3.6 when Family < 1.2 & Economy < 0.49 & Freedom < 0.24. This group covers 6% of the total, which has 9 countries in this classification. Thus, totally, we have ten rules to classify the countries in the world.

```{r}
# generating tree plot for all countries in the world 156
fancyRpartPlot(reg.dt.all)
```

```{r}
pred.dt = predict(reg.dt, newdata = test.set)
pred.actual.dt = as.data.frame(cbind(Prediction = pred.dt, Actual = test.set$Happiness.Score))
error = accuracy(pred.dt, test.set$Happiness.Score)
rmse.dt = format(round(error[2], 4), nsmall = 4) %>% as.numeric()
gg.dt = ggplot(pred.actual.dt, aes(x = Actual, y = Prediction)) +
    geom_point() + theme_bw() + geom_abline() +
    labs(title = "Decision Tree", subtitle = paste0("RMSE: ", rmse.dt),
         x = "Actual happiness score", y = "Predicted happiness score") +
    theme(plot.title = element_text(face = "bold", size = (15)),
          plot.subtitle = element_text(size = (10)),
          axis.title = element_text(size = (10)))
gg.dt
```

#### Random Forest <a name = "4.2.4"></a>

```{r}
set.seed(123)
reg.rf = randomForest(x = train.set[, -1], y = train.set$Happiness.Score, ntree = 500)
```

```{r}
pred.rf = predict(reg.rf, newdata = test.set)
pred.actual.rf = as.data.frame(cbind(Prediction = pred.rf, Actual = test.set$Happiness.Score))
error = accuracy(pred.rf, test.set$Happiness.Score)
rmse.rf = format(round(error[2], 4), nsmall = 4) %>% as.numeric()
gg.rf = ggplot(pred.actual.rf, aes(x = Actual, y = Prediction)) +
    geom_point() + theme_bw() + geom_abline() +
    labs(title = "Random Forest", subtitle = paste0("RMSE: ", rmse.rf),
         x = "Actual happiness score", y = "Predicted happiness score") +
    theme(plot.title = element_text(face = "bold", size = (15)),
          plot.subtitle = element_text(size = (10)),
          axis.title = element_text(size = (10)))
gg.rf
```

#### Neural Net <a name = "4.2.5"></a>

```{r}
set.seed(123)
reg.nn = neuralnet(formula = Happiness.Score ~ .,
                   data = train.set,
                   hidden = c(2, 1, 2),
                   stepmax = 1e+6,
                   linear.output = T)
```

```{r}
pred.nn = compute(reg.nn, test.set[, 2:7])
pred.actual.nn = as.data.frame(cbind(Prediction = pred.nn$net.result, Actual = test.set$Happiness.Score))
colnames(pred.actual.nn) = c("Prediction", "Actual")
error = accuracy(pred.actual.nn$Prediction, pred.actual.nn$Actual)
rmse.nn = format(round(error[2], 4), nsmall = 4) %>% as.numeric()
gg.nn = ggplot(pred.actual.nn, aes(x = Actual, y = Prediction)) +
    geom_point() + theme_bw() + geom_abline() +
    labs(title = "Neural Net", subtitle = paste0("RMSE: ", rmse.nn),
         x = "Actual happiness score", y = "Predicted happiness score") +
    theme(plot.title = element_text(face = "bold", size = (15)),
          plot.subtitle = element_text(size = (10)),
          axis.title = element_text(size = (10)))
gg.nn
```

### Evaluation <a name = "4.3"></a>

```{r, fig.width = 10, fig.height = 7.5}
ggarrange(gg.rf, gg.nn, gg.svr, gg.mlr, gg.dt, nrow = 2, ncol = 3)
```

```{r, fig.width = 3, fig.height = 1}
rmse = as.data.frame(cbind(MLR = rmse.mlr, SVR = rmse.svr, DT = rmse.dt, RF = rmse.rf, NN = rmse.nn))
rmse %>% mutate(across(is.numeric, ~ round(., 2))) %>% ggtexttable(rows = "RMSE", theme = ttheme("classic"))
```

```{r, fig.width = 6, fig.height = 4}
rmse %>% t() %>% as.data.frame() %>% arrange(V1) %>% 
    mutate(ml.name = factor(c("RF", "NN", "SVR", "MLR", "DT"),
                            levels = c("RF", "NN", "SVR", "MLR", "DT"))) %>% 
    ggplot(aes(x = ml.name, y = V1)) + 
    geom_bar(stat = "identity", width = 0.7) +
    theme_bw() +
    coord_cartesian(ylim = c(0.4, 0.6)) +
    labs(title = "RMSE for different machine learning algorithms", y = "RMSE", x = NULL) +
    theme(plot.title = element_text(face = "bold", size = (15)),
          axis.title = element_text(size = (10)))
```

## Conclusion <a name = "5"></a>

Although Australia has the highest Happiness.Score in any variable consideration, the insight is not meaningful at all due to lacking of enough sample size in the group. Therefore, North America is the happiest continent in the world. However, it is not a equally condition. The most equally happy continent in fact is Europe. There are some insights worthying to discuss. Firstly, Generosity surprisingly is not an impactful factor to contribute Happiness.Score. Secondly, the best regression is the neural random forest regression model. In the future, we can use this model to predict a new country or a new year index.

## Reference <a name = "6"></a>

1. [World Happiness Report - Keggle](https://tinyurl.com/yxsfrkr3) 
2. [Happiness 2017 - Javad Zabihi](https://tinyurl.com/y28gso55)
